Turbulence in compact to giant HII regions

### 2021-10-13 strucfunc_paper.tex
Add figures for inner and outer observed scales

\section{Introduction}
\WILL{I think it would be best to lead with a description of the dynamics of H II regions before mentioning the turbulence}.

@@

%\appendix

>>>>

\section{Introduction}

\WILL{I think it would be best to lead with a description of the dynamics of H II regions before mentioning the turbulence}.

@@

\appendix

\section{Degradation of the structure function due to observational limitations}
\label{sec:degr-struct-funct}

\subsection{Finite box effects}
\label{sec:finite-box-effects}

\begin{figure}
  \begin{tabular}{@{} l @{}}
    (a)\\
    \includegraphics[width=\linewidth]{Figures/fake-finite-box-images}
    \\[\bigskipamount]
    (b)\\
    \includegraphics[width=\linewidth]{Figures/fake-finite-box-strucfunc}
  \end{tabular}
  \caption{Effects of finite box size on the structure function.
    (a)~Construction of simulated turbulent velocity fields of different sizes
    by repeated division of an initial field of size \(512 \times 512\) pixels.
    The \(j\)th level of division yields \(N = 4^j\) fields,
    each of linear size \(L \times L\) where \(L = 2^{9 - j}\). 
    (b)~Resultant structure functions.
  }
  \label{fig:finite-box}
\end{figure}

\begin{figure}
  \includegraphics[width=\linewidth]{Figures/fake-finite-box-effect}
  \caption{
    Reduction of apparent velocity variance and correlation length
    due to finite box size.
  }
  \label{fig:finite-box-effect}
\end{figure}

\subsection{Effects of seeing}
\label{sec:effects-seeing-struc}

\begin{figure}
  \begin{tabular}{@{} l @{}}
    (a)\\
    \includegraphics[width=\linewidth]{Figures/fake-seeing-nonp-thumbnails}\\
    (b)\\
    \includegraphics[width=\linewidth]{Figures/fake-seeing-nonp-reduction}
  \end{tabular}
  \caption{Effects of seeing on the structure function.
    (a)~Each row shows a different simulated random velocity field on a \(256^2\) grid
    (see text for details).
    The left column shows the original field,
    while the remaining columns show the effects of smoothing by a gaussian kernel
    with RMS width \(s_0\) from 1 to 32 pixels.
    The same color scale is used for all columns, ranging from \(-3\) to \(+3\) times
    the standard deviation of the unsmoothed map.
    (b)~Relative change in the second-order structure function due to the gaussian smoothing.
    Solid lines with symbols show the average over the 4 maps of
    \(B(r, s_0) / B(r, s_0 = 0)\) as a function of separation \(r\),
    with a separation of \(2 s_0\) indicated by a large filled circle on each curve.
    Dashed lines shows the empirical fit discussed in the text.
    The dotted line shows the correlation length of the original fields,
    while colored plus symbols show the apparent correlation length of the smoothed fields.
  }
  \label{fig:seeing-reduction}
\end{figure}
